Relict populations of a deciduous oak show high resilience to drought despite land-use legacies

### 2018-10-09 man/report.Rmd
update
remove supp figures from repor rmd
prepare v2

---
title: "ms_borrador"
author: "AJ Perez-Luque; G. Gea-Izquierdo; R. Zamora; FJ. Bonet"
date: "2017"
output:  word_document
bibliography: ../references.bib
csl: ../ecology.csl
---

@@

>>>>

---
title: "Relict populations of a deciduous oak show high resilience to drought despite land-use legacies"
author: "AJ Perez-Luque; G. Gea-Izquierdo; ..."
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    highlight: null
    reference_docx: template_ms.docx
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

# Abstract 
* Trees showed resilience to drought events, despite the ‘a priori’ vulnerability that they can express as a result of the impact of climate change on relict stands resulting from intensive land-use in history.

* Oak resilience to drought followed a dryness gradient: Northern populations, which thrive under a drier climate, were less resilient to drought both in primary and secondary growth than Southern populations where lower altitudes were also less resilient than those at high-altitudes.

@@

```{r child = 'ms_3_discussion.Rmd'}
```
